Community comparison

### 2019-12-23 code/community.Rmd
change colors in stacked barplots

```{r rotated-stacked-bar, echo=F}
# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#984ea3","Chlainomonas rubra"="#984ea3", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                "Chloromonas krienitzii"="#ff7f00","Chloromonas muramotoi C"="#173416", "Chloromonas D"="#265725", "Chloromonas cf. brevispina"="forestgreen", "Chloromonas cf. nivalis"="lightgreen","Chloromonas F"="#b25800", #greens
                "Other Chloromonas"="#4daf4a", "Chloromonas"="#4daf4a", #light greens
                "Trebouxiophyceae G"="#377eb8", "Trebouxiophyceae"="#377eb8", # blue
                "Unknown E"="grey40", "Green cell"="#b2d8b2", "Other"="grey70") #greys
# backwards
species_colors <- species_colors %>% rev()

@@

stacked_bar +
  theme(legend.position="none")
```

>>>>

```{r, fig.width=2, fig.height=2}
chloromonas_color <- "#4daf4a" # green
krienitzii_color <- "#ff7f00" # orange
muramotoi_color <- "#d7d42e" # yellow
# pick shades using https://www.color-hex.com/
hohamii_and_D_color <- "#265725" # dark green
group_B_and_F_color <- "#b25800" # brown
chloromonas_colors <- c(chloromonas_color, krienitzii_color, muramotoi_color, hohamii_and_D_color,group_B_and_F_color)
scales::show_col(chloromonas_colors)
scales::show_col("#4aaf53")

```{r rotated-stacked-bar, echo=F, fig.width=7, fig.height=5}

# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#984ea3","Chlainomonas rubra"="#984ea3", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                # Chloromonas: pastel greens / blues / yellows
                "Chloromonas krienitzii"="#ff7f00","Chloromonas muramotoi C"="#87b1d4", "Chloromonas D"="#94cf92", "Chloromonas F"="#fdfd96", 
                #    orange green                                      pale blu,                   blue green      yellow--only high elev
                "Chloromonas cf. brevispina"="#80c786", "Chloromonas cf. nivalis"="#4aaf86", 
                #                 lt green                            teal
                "Other Chloromonas"="#4aaf53", "Chloromonas"="#4aaf53", 
                # greyish light green
                "Trebouxiophyceae G"="#173416", "Trebouxiophyceae"="#173416", # dark green, stand out
                "Unknown E"="grey60", "Green cell"="#4aaf53", "Other"="grey30") #greys

# teal #69c095
# medium blue #6994c0

# backwards
species_colors <- species_colors %>% rev()

@@

stacked_bar +
  theme(legend.position="none")
#18s: check
# cellct: _
# rbcl: _
```
